\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-07-30 docs/parco13/paper.tex

@@

In both sets of numerical results, we solve a scalar advection
equation,
\begin{equation}
q_t + ({\bf u}\cdot \nabla) q = 0 ,
\end{equation}
where the velocity field ${\bf u} = (u(\xi,\eta,t), v(\xi,\eta,t)$ is
a prescribed function of computational coordinates.  The relevant
numerical parameters that are set in each case include the size of the
patch on each leaf ($m=8$ in each case), and the minimum and maximum
refinement levels, which in turn fix minimum and maximum effective grid
resolutions.

>>>>

\alert{Thought: Should we swap sections 3. and 4.?}

@@

In both sets of numerical results, we solve a scalar advection
equation,
\begin{equation}
q_t + ({\bf u}\cdot \nabla) q = 0 ,
\end{equation}
where the velocity field ${\bf u} = (u(\xi,\eta,t), v(\xi,\eta,t)$ is
a prescribed function of computational coordinates.  The relevant
numerical parameters that are set in each case include the size of the
patch on each leaf ($m=8$ or $m=16$), and the minimum and maximum
refinement levels, which in turn fix minimum and maximum effective grid
resolutions.
